PANCHANGE_descriptives

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Added a phq retro prepan scatterplot for the whole sample

```{r Whole sample scatterplot for gad prepan base}

@@

whole_retro_prepan_scatter <- dat %>% 
  filter(gad.pandemic_felt_feelings == "Much worse" |
           gad.pandemic_felt_feelings == "A little worse" |
           gad.pandemic_felt_feelings == "A little better" |
           gad.pandemic_felt_feelings == "Much better")

whole_retro_prepan_scatter %>% ggplot(aes(x = gad.sum_score_retro, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4)

>>>>

```{r Whole sample scatterplots for gad and phq prepan retro}

@@

whole_retro_prepan_gad_scatter <- whole_retro_prepan_scatter %>% 
  filter(gad.pandemic_felt_feelings == "Much worse" |
           gad.pandemic_felt_feelings == "A little worse" |
           gad.pandemic_felt_feelings == "A little better" |
           gad.pandemic_felt_feelings == "Much better")

whole_retro_prepan_phq_scatter <- whole_retro_prepan_scatter %>% 
  filter(gad.pandemic_felt_feelings == "Much worse" |
           gad.pandemic_felt_feelings == "A little worse" |
           gad.pandemic_felt_feelings == "A little better" |
           gad.pandemic_felt_feelings == "Much better")

#Visualise as scatterplots

whole_retro_prepan_gad_scatter %>% ggplot(aes(x = gad.sum_score_retro, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor whole sample",
                      sep=" "),
        subtitle = paste("n", dim(whole_retro_prepan_gad_scatter)[1]))

whole_retro_prepan_gad_scatter %>% ggplot(aes(x = phq.sum_score_retro, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor whole sample",
                      sep=" "),
        subtitle = paste("n", dim(whole_retro_prepan_gad_scatter)[1]))
